Structuring College Access

### 2025-06-27 index.qmd
remove mean income from rq1 table

  var_order <- c(
    '% White, non-Hispanic', '% Asian, non-Hispanic', '% Black, non-Hispanic', '% Hispanic',
    '% Two+, non-Hispanic', '% NHPI, non-Hispanic', '% AIAN, non-Hispanic',
    'Median income', 'Mean income', '% in poverty', '% with BA+'
  )

>>>>

  var_order <- c(
    '% White, non-Hispanic', '% Asian, non-Hispanic', '% Black, non-Hispanic', '% Hispanic',
    '% Two+, non-Hispanic', '% NHPI, non-Hispanic', '% AIAN, non-Hispanic',
    'Median income', '% in poverty', '% with BA+'
  )
